
---
title: "Data Cleaning"
output: html_document
date: "2024-04-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required libraries
library(readr)
library(dplyr)
library(ggplot2)

# Read the CSV file while suppressing column type messages
data <- read_csv("../data/latest_data_set.csv", show_col_types = FALSE)



# Check column names
names(data)
```

```{r}
# Count NA values in each column
null_values <- sapply(data, function(x) sum(is.na(x)))
print(null_values)
```

```{r}
# Fix column name typo
names(data)[names(data) == "influencer_inspired_travel _frequency"] <- "influencer_inspired_travel_frequency"

# Replace NAs in specific columns with "Not Applicable"
columns_to_clean <- c("Intl_students", "degree", "avg_watch_time_livestream",
                      "watched_livestream_frequency", "purchase_frequency",
                      "influencer_inspired_travel_frequency")

for (col in columns_to_clean) {
  data[[col]][is.na(data[[col]])] <- "Not Applicable"
}

# Check again for remaining NAs
sapply(data[columns_to_clean], function(x) sum(is.na(x)))
```

```{r}
# Summary and structure
summary(data)
str(data)
```

```{r}
# Categorical variable summaries
table(data$gender)
table(data$age_group)
table(data$occupation)
table(data$degree)
table(data$follow_influencers)
table(data$purchased_product)
```

```{r}
# Visualize Gender Distribution
ggplot(data, aes(x = gender, fill = gender)) +
  geom_bar(width = 0.4) +
  labs(title = "Distribution of Gender", x = "Gender", y = "Count") +
  scale_fill_manual(values = c(
    "Male" = "#1b9e77", "Female" = "#d95f02", "Other" = "#7570b3",
    "Prefer not to say" = "#e7298a", "Prefer to self-describe" = "#66a61e"
  ))
```

```{r}
# Age Group Distribution
ggplot(data, aes(x = age_group, fill = age_group)) + 
  geom_bar(width = 0.4) +
  labs(title = "Distribution of Age Group", x = "Age Group", y = "Count") +
  scale_fill_manual(values = c(
    "18-24" = "#1b9e77", "25-34" = "#d95f02", "35-44" = "#7570b3",
    "45-54" = "#e7298a", "55-64" = "#66a61e", "65+" = "#000080"
  ))
```
> Visual analysis revealed that male users and individuals aged 35–44 were the most represented in the dataset. These insights suggest demographic trends in short-video platform engagement.

```{r}
# Influencer Following and Purchases
ggplot(data, aes(x = follow_influencers, fill = purchased_product)) +
  geom_bar(position = "dodge", width = 0.4) +
  labs(title = "Product Purchases by Influencer Following",
       x = "Following Influencers", y = "Count of Responses") +
  scale_fill_manual(values = c("Yes" = "#1b9e77", "No" = "#d95f02"))
```

```{r}
# Chi-squared test
data$follow_influencers <- as.factor(data$follow_influencers)
data$purchased_product <- as.factor(data$purchased_product)

contingency_table <- table(data$follow_influencers, data$purchased_product)
chi_squared_test <- chisq.test(contingency_table)
print(chi_squared_test)
```
> A chi-squared test for independence revealed a significant association between following influencers and purchasing products (χ² = 127.92, df = 1, p < 0.001). This suggests that users who follow influencers are significantly more likely to make influencer-driven purchases than those who do not.

```{r}
# Emotional fulfillment vs. following influencers
table_fulfillment <- table(data$emotional_fullfillment, data$follow_influencers)
chisq.test(table_fulfillment)
```
> The chi-squared test also revealed a significant association between emotional fulfillment and following influencers (χ² = 8.80, df = 2, p = 0.012), suggesting that emotional engagement is linked to influencer interaction.


```{r}
# Bar plot for emotional fulfillment
ggplot(data, aes(x = follow_influencers, fill = emotional_fullfillment)) +
  geom_bar(position = "fill", width = 0.4) +
  labs(title = "Emotional Fulfillment by Influencer Following",
       x = "Follow Influencers", y = "Proportion") +
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
# Logistic Regression
data$follow_influencers <- ifelse(data$follow_influencers == "Yes", 1, 0)
data$purchased_product <- ifelse(data$purchased_product == "Yes", 1, 0)

data$follow_influencers <- as.factor(data$follow_influencers)
data$purchased_product <- as.factor(data$purchased_product)

logit_model <- glm(purchased_product ~ follow_influencers, family = binomial(), data = data)
summary(logit_model)

# Odds ratio
exp(coef(logit_model))
```
> A binary logistic regression confirmed that following influencers significantly predicts the likelihood of purchasing a product (p < 0.001). The odds ratio (17.23) indicates that influencer-followers are over 17 times more likely to make purchases than non-followers.

